### 2013-09-27 nyu/paper.tex
remove typos, thank vlad some more :)
Fix figure allignment in nyu
some moving around of figures and tables
k-means not capitalizes, minor fixes

\begin{figure}
    \begin{center}
        \includegraphics[width=\linewidth]{nyu/images/height_success}\\
        \vspace{3mm}
        \includegraphics[width=\linewidth]{nyu/images/height_failure}
    \end{center}
    \caption{%
        Visualization of the height computed using the method described in \Secref{unaries}.
        Input images are shown on the left (depth not shown), the computed height is depicted on the right.
        The top row exemplifies a typical scene, while the bottom row shows a scene without horizontal
        surfaces, where our method fails.
    \figlabel{height}}
\end{figure}

\subsection{Low Level Segmentation}
We take a super-pixel based approach to semantic segmentation.
Our superpixel generation is based on the SLIC
algorithm~\citep{achanta2012slic} described in \Secref{semantic_segmentation}. We
extend the standard SLIC algorithm, which works on the Lab space, to also
include depth information. The resulting algorithm is a localized $k$-Means in
Lab-D-XY space.
Our implementation is publicly available through the scikit-image library\footnote{\url{http://scikit-image.org}}.
Similar to \citet{SilbermanECCV12}, we found little visual improvement over the
RGB segmentation when using additional depth information. On the other hand,
estimation of per-superpixel features based on the 3D point cloud was more
robust when including depth information into the superpixel procedure.
%TODO visualize?
The resulting superpixels are compact in the 2D image. As the density of the
corresponding point cloud is dependent on the depth, we did not succeed in
creating superpixels that are compact in 3D while maintaining a meaningful
minimum size.

\subsection{Unary Image Features}\seclabel{unaries}
Our method builds on the probability output of a random forest, trained for pixel-wise
classification of the structure classes.
We use the GPU implementation provided by \citet{stueckler2013}\footnote{\url{https://github.com/deeplearningais/curfil}}.
The input for training are the full \mbox{RGB-D} images, transformed to Lab
color space. Each tree in the forest uses training pixels only from a subset of
training images. For each training image, an equal number of pixels for each
occurring class is sampled. Split features are given by difference of regions
on color or depth channels. Region size and offsets are normalized using the
depth at the target pixel.
We accumulate the probabilistic output for all pixels within a superpixel, and
use the resulting distribution as a feature for the unary node potentials in our CRF model.
We augment these prediction with another feature, based on the height of a superpixel in 3D.
This is a very informative feature, in particular to determine the floor.
To compute the height of a (super) pixel, we first find the ``up'' direction.
We use a very simple approach that we found effective: we cluster normal
directions of all pixels into 10 clusters using $k$-means, and use the one that
is most parallel to the $Y$ direction, which roughly corresponds to height in
the dataset.
We then project the 3D point cloud given by the depth along this direction, and
normalize the result between $0$ and $1$.
This procedure works robustly given there is some horizontal surface in the image,
such as the ground or a table. A few scenes contain only walls and furniture,
and the approach fails for these. \Figref{height} illustrates a typical case and
one of the much rarer failure cases.
While we could use a more elaborate scheme,
such as the one from \citet{SilbermanECCV12}, we suspect that the feature is of
little use in scenes without horizontal surfaces.
\begin{figure}
    \begin{center}
        \includegraphics[width=\linewidth]{nyu/images/normal_feature}
    \end{center}
    \caption{%
        Visualization of one of the pairwise features, the similarity between superpixel normals.
        The image shows the zoom-in of a bedroom scene, together with the superpixel over-segmentation.
        Lines connect adjacent superpixels, and line-strength gives the magnitude of the orientation similarity.
    \figlabel{normal_feature}}
\end{figure}

@@

\begin{table*}[t]
\begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}l@{}cccccc}
\toprule
                        & \footnotesize{ground}        &  \footnotesize{structure}    & \footnotesize{furniture}     & \footnotesize{props}         & \footnotesize{class avg.}   & \footnotesize{pixel avg.}\\
\cmidrule{1-7}

@@

We evaluate our approach on the public NYU depth V2 segmentation dataset of
indoor scenes.  The dataset comes with a detailed annotation of 1449 indoor
\mbox{RGB-D} images belonging to a wide variety of indoor scenes, categorized into 26
scene classes.  The annotation contains four semantic structural classes:
structure, floor, furniture and prop. As in the MSRC-21 and \textsc{Pascal} VOC
datasets, there is an additional ``void'' class, which is used for object
boundaries and hard-to-annotate regions. We follow the
literature in excluding these pixels completely from the evaluation.
We optimize our model for \emph{average class accuracy} (the mean of the
diagonal of the confusion matrix), which puts more emphasis on the harder
classes of props and furniture, which have smaller area than structure and
floor.

Our approach is implemented using our \textsc{PyStruct}
library introduced in \Secref{pystruct}.
%
All hyper parameters were adjusted using 5-fold cross-validation. The
hyper parameters of the random forests were found using the \textsc{hyperopt}
framework of \citet{bergstra2011algorithms}. For the CRF model, the only
hyper-parameters are related to the superpixel segmentation, and the single
hyper-parameter $C$ of the structural SVM formulation. These were adjusted
using grid-search.
We found 500 superpixels per image to work best, which allow for a maximum
possible performance of 95\% average class accuracy on the validation set.

@@

\Tabref{results} compares different components of our approach with the literature.
Please note that we \emph{first} designed our final model, using only the
validation data. We now report accuracies of simpler models for reference,
however these results were not used for model selection. To separate
the influence of loss-based training and the spatial reasoning of the CRF,
we also train a usual support vector machine (SVM) on the unary potentials for comparison.

@@

We found that our approach improves results most for scenes with a clear geometric structure,
which is not surprising. We see that evidence from the random forest is often very noisy, and biased
away from the ``props'' class. While the unstructured SVM can correct somewhat
for the class imbalance, it has no way to make larger areas consistent, which
the CRF can.
On the other hand, performance of the CRF deteriorates slightly on very crowded
scenes with a mixture of small furniture and prop objects, as
can be seen in the two right-most images. In these scenes, depth information is
often noisy, and it is hard to make geometric statements on the superpixel
level. As the input from the random forest is also often of low quality for
crowded scenes, the CRF has little chance to recover.
%
\begin{figure}
    \begin{center}
        \includegraphics[width=.45\linewidth]{nyu/images/vertical_alignment}
    \includegraphics[width=.45\linewidth]{nyu/images/depth_difference}
    \end{center}
    \caption{%
        Visualization of some of the learned potentials. The right potential is
        applied to relative depth between superpixels, the second on the
        feature encoding whether one superpixel is above the other in the
        image. See \secref{experiments} for details.
    \figlabel{weights}}
\end{figure}
%
\Figref{weights} visualizes some learned potential functions.
Higher values correspond to favored configurations. One can see that the
vertical alignment potential expresses that the floor is much more likely to be below
other classes. It also encodes the fact that props
rest on furniture, but not the other way around.
The potential of the depth feature encodes, for example, that the ground
is usually behind the other classes, while furniture is in front of structures,
such as the wall.
Interestingly, the potential functions are not anti-symmetric, and forcing them to be so
degrades the results. This suggests that the direction of connecting edges, going from
the top left to the bottom right in the image, is also exploited by the potentials.

>>>>

\begin{figure}[t]
    \begin{center}
        \includegraphics[width=\linewidth]{nyu/images/height_success}\\
        \vspace{3mm}
        \includegraphics[width=\linewidth]{nyu/images/height_failure}
    \end{center}
    \caption{%
        Visualization of the height computed using the method described in \Secref{unaries}.
        Input images are shown on the left (depth not shown), the computed height is depicted on the right.
        The top row exemplifies a typical scene, while the bottom row shows a scene without horizontal
        surfaces, where our method fails.
    \figlabel{height}}
\end{figure}

\subsection{Low Level Segmentation}
We take a super-pixel based approach to semantic segmentation.
Our superpixel generation is based on the SLIC
algorithm~\citep{achanta2012slic} described in \Secref{semantic_segmentation}. We
extend the standard SLIC algorithm, which works on the Lab space, to also
include depth information. The resulting algorithm is a localized $k$-means in
Lab-D-XY space.
Our implementation is publicly available through the scikit-image library\footnote{\url{http://scikit-image.org}}.
Similar to \citet{SilbermanECCV12}, we found little visual improvement over the
RGB segmentation when using additional depth information. On the other hand,
estimation of per-superpixel features based on the 3D point cloud was more
robust when including depth information into the superpixel procedure.
%TODO visualize?
The resulting superpixels are compact in the 2D image. As the density of the
corresponding point cloud is dependent on the depth, we did not succeed in
creating superpixels that are compact in 3D while maintaining a meaningful
minimum size.

\subsection{Unary Image Features}\seclabel{unaries}
Our method builds on the probability output of a random forest, trained for pixel-wise
classification of the structure classes.
We use the GPU implementation provided by \citet{stueckler2013}\footnote{\url{https://github.com/deeplearningais/curfil}}.
The input for training are the full \mbox{RGB-D} images, transformed to Lab
color space. Each tree in the forest uses training pixels only from a subset of
training images. For each training image, an equal number of pixels for each
occurring class is sampled. Split features are given by difference of regions
on color or depth channels. Region size and offsets are normalized using the
depth at the target pixel.
We accumulate the probabilistic output for all pixels within a superpixel, and
use the resulting distribution as a feature for the unary node potentials in our CRF model.
We augment these prediction with another feature, based on the height of a superpixel in 3D.
This is a very informative feature, in particular to determine the floor.
To compute the height of a (super) pixel, we first find the ``up'' direction.
We use a very simple approach that we found effective: we cluster normal
directions of all pixels into $10$ clusters using $k$-means, and use the one that
is most parallel to the $Y$ direction, which roughly corresponds to height in
the dataset.
We then project the 3D point cloud given by the depth along this direction, and
normalize the result between $0$ and $1$.
This procedure works robustly given there is some horizontal surface in the image,
such as the ground or a table. A few scenes contain only walls and furniture,
and the approach fails for these. \Figref{height} illustrates a typical case and
one of the much rarer failure cases.
While we could use a more elaborate scheme,
such as the one from \citet{SilbermanECCV12}, we suspect that the feature is of
little use in scenes without horizontal surfaces.
\begin{figure}[tb]
    \begin{center}
        \includegraphics[width=\linewidth]{nyu/images/normal_feature}
    \end{center}
    \caption{%
        Visualization of one of the pairwise features, the similarity between superpixel normals.
        The image shows the zoom-in of a bedroom scene, together with the superpixel over-segmentation.
        Lines connect adjacent superpixels, and line-strength gives the magnitude of the orientation similarity.
    \figlabel{normal_feature}}
\end{figure}

@@

\begin{table*}[t]
\begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}l@{}cccccc}
\toprule
                        & \footnotesize{ground}        &  \footnotesize{structure}    & \footnotesize{furniture}     & \footnotesize{prop}         & \footnotesize{class avg.}   & \footnotesize{pixel avg.}\\
\cmidrule{1-7}

@@

We evaluate our approach on the public NYU depth V2 segmentation dataset of
indoor scenes.  The dataset comes with a detailed annotation of 1449 indoor
\mbox{RGB-D} images belonging to a wide variety of indoor scenes, categorized into 26
scene classes.  The annotation contains four semantic structural classes:
structure, floor, furniture and prop. As in the MSRC-21 and \textsc{Pascal} VOC
datasets, there is an additional ``void'' class, which is used for object
boundaries and hard-to-annotate regions. We follow the
literature in excluding these pixels completely from the evaluation.
We optimize our model for \emph{average class accuracy} (the mean of the
diagonal of the confusion matrix), which puts more emphasis on the harder
classes of prop and furniture, which have smaller area than structure and
floor.

Our approach is implemented using our \textsc{PyStruct}
library introduced in \Secref{pystruct}.
%
All hyper-parameters were adjusted using 5-fold cross-validation. The
hyper parameters of the random forests were found using the \textsc{hyperopt}
framework of \citet{bergstra2011algorithms}. For the CRF model, the only
hyper-parameters are related to the superpixel segmentation, and the single
hyper-parameter $C$ of the structural SVM formulation. These were adjusted
using grid-search.
We found 500 superpixels per image to work best, which allow for a maximum
possible performance of 95\% average class accuracy on the validation set.

@@

\Tabref{results} compares different components of our approach with the literature.
Note that we \emph{first} designed our final model, using only the
validation data. We now report accuracies of simpler models for reference,
however these results were not used for model selection. To separate
the influence of loss-based training and the spatial reasoning of the CRF,
we also train a usual support vector machine (SVM) on the unary potentials for comparison.

@@

We found that our approach improves results most for scenes with a clear geometric structure,
which is not surprising. We see that evidence from the random forest is often very noisy, and biased
away from the ``prop'' class. While the unstructured SVM can correct somewhat
for the class imbalance, it has no way to make larger areas consistent, which
the CRF can.
On the other hand, performance of the CRF deteriorates slightly on very crowded
scenes with a mixture of small furniture and prop objects, as
can be seen in the two right-most images. In these scenes, depth information is
often noisy, and it is hard to make geometric statements on the superpixel
level. As the input from the random forest is also often of low quality for
crowded scenes, the CRF has little chance to recover.
%
\begin{figure}
    \begin{center}
        \includegraphics[height=.40\linewidth]{nyu/images/vertical_alignment}
    \includegraphics[height=.40\linewidth]{nyu/images/depth_difference}
    \end{center}
    \caption{%
        Visualization of some of the learned potentials. The right potential is
        applied to relative depth between superpixels, the second on the
        feature encoding whether one superpixel is above the other in the
        image. See \secref{experiments} for details.
    \figlabel{weights}}
\end{figure}
%
\Figref{weights} visualizes some learned potential functions.
Higher values correspond to favored configurations. One can see that the
vertical alignment potential expresses that the floor is much more likely to be below
other classes. It also encodes the fact that prop
rest on furniture, but not the other way around.
The potential of the depth feature encodes, for example, that the ground
is usually behind the other classes, while furniture is in front of structures,
such as the wall.
Interestingly, the potential functions are not anti-symmetric, and forcing them to be so
degrades the results. This suggests that the direction of connecting edges, going from
the top left to the bottom right in the image, is also exploited by the potentials.

### 2013-09-27 partial_supervision/paper.tex
k-means not capitalizes, minor fixes

\section{Related Work}
\subsection{Object Segment Proposals}\label{related_segments}
Most work on multi-class segmentation focuses on strong supervision on
superpixel level. There is still little work on using candidate segments.  The
method we use for generating candidate segments is Constraint Parametric
Min-Cuts (CPMC) from \citet{carreira2010constrained}.  This method creates a
wide variety of overlapping segments. Support vector regression (SVR) is
trained on these segments to estimate the overlap of segments with ground truth
object-class labeling from the \textsc{Pascal} VOC dataset~\citep{pascal}. This provides
a ranking of candidate segments according to how ``object-like'' they are,
which allows for selecting only a limited number of very object-like segments.
The method performed well on a variety of datasets, building the basis of
a very successful entry to the \textsc{Pascal} VOC segmentation
challenge~\citep{li2010object}. A similar approach to whole-object segment
proposals was investigated by \citet{endres2010category}, but they did not compare
their results with the state-of-the-art approach of \citet{carreira2010constrained}.
%Brendel and Todorovic~\citet{NIPS2010_0122} also use a set of candidate segments is used, though all of these are kept throughout the whole 
%algorithm.

@@

\section{Multi-Instance Kernels for Image Segmentation}
\subsection{Constraint Parametric Min-Cuts (CPMC)}
% Repetition?
To generate proposal segments, we use the Constraint Parametric Min-Cuts (CPCM)
method from \citet{carreira2010constrained}. In CPMC, initial segments are
constructed using graph cuts on the pixel grid. The energy function for these cuts
uses pixel color and the response of the global probability of boundary (gPb)
detector~\citep{maire2008using}. As much as ten thousand initial segments are
generated from foreground and background seeds. A fast rejection based on
segment size and ratio cut~\citep{wang2003image} reduces these to about 2000
overlapping segments per image. Then, the segments are ranked according to a
measure of object-likeness that is based on region and Gestalt properties.
This ranking is computed using an SVR model~\citep{carreira2010constrained},
which is available online. 
% TODO implementation detail?
\enlargethispage{10mm}
For computing the global probability of boundary
(gPb), we used the CUDA implementation of \citet{catanzaro2009efficient}, which
provides a speedup of two orders of magnitude over the original implementation.

>>>>

\section{Related Work}
\subsection{Object Segment Proposals}\label{related_segments}
Most work on multi-class segmentation focuses on strong supervision on
superpixel level. There is still little work on using candidate segments.  The
method we use for generating candidate segments is Constraint Parametric
Min-Cuts (CPMC) of \citet{carreira2010constrained}.  This method creates a
wide variety of overlapping segments. Support vector regression (SVR) is
trained on these segments to estimate the overlap of segments with ground truth
object-class labeling from the \textsc{Pascal} VOC dataset~\citep{pascal}. This provides
a ranking of candidate segments according to how ``object-like'' they are,
which allows for selecting only a limited number of very object-like segments.
The method performed well on a variety of datasets, building the basis of
a very successful entry to the \textsc{Pascal} VOC segmentation
challenge~\citep{li2010object}. A similar approach to whole-object segment
proposals was investigated by \citet{endres2010category}, but they did not compare
their results with the state-of-the-art approach of \citet{carreira2010constrained}.
%Brendel and Todorovic~\citet{NIPS2010_0122} also use a set of candidate segments is used, though all of these are kept throughout the whole 
%algorithm.

@@

\section{Multi-Instance Kernels for Image Segmentation}
\subsection{Constraint Parametric Min-Cuts (CPMC)}
% Repetition?
To generate proposal segments, we use the Constraint Parametric Min-Cuts (CPCM)
method of \citet{carreira2010constrained}. In CPMC, initial segments are
constructed using graph cuts on the pixel grid. The energy function for these cuts
uses pixel color and the response of the global probability of boundary (gPb)
detector~\citep{maire2008using}. As much as ten thousand initial segments are
generated from foreground and background seeds. A fast rejection based on
segment size and ratio cut~\citep{wang2003image} reduces these to about 2000
overlapping segments per image. Then, the segments are ranked according to a
measure of object-likeness that is based on region and Gestalt properties.
This ranking is computed using an SVR model~\citep{carreira2010constrained},
which is available online. 
% TODO implementation detail?
\enlargethispage{10mm}
For computing the global probability of boundary
(gPb), we used the CUDA implementation of \citet{catanzaro2009efficient}, which
provides a speedup of two orders of magnitude over the original implementation.

### 2013-09-27 pystruct/paper.tex
move interesting phenomenon back to letters.
k-means not capitalizes, minor fixes

\bottomrule
\end{tabularx}
    \caption{\label{table:comparision_algorithms}Comparison of learning
        algorithms implemented in popular structured prediction software
        packages. 1-CP stands for 1-slack Cutting Plane, $n$-CP for $n$-slack
        Cutting plane, SSGD for stochastic subgradient decent learning of
        SSVMs, SZLJSP is as described in \secref{dual_coordinate_descent},
        L-SVM stands for latent variable SSVMs, and ML for
        maximum likelihood learning.}
\end{table}

@@

We demonstrate the use of \pystruct on the task of semantic image segmentation,
the main focus of this work. The example shows how to learn an $n$-slack support
vector machine on a superpixel-based CRF on the \textsc{Pascal VOC} dataset. Details of the experiment
can be found in Section~\secref{semantic_segmentation}.
Each sample (corresponding on one entry of the list \texttt{X}) is represented as a
tuple consisting of input features and a graph representation.
\begin{listing}[t]
\begin{pythoncode}
model = crfs.EdgeFeatureGraphCRF(
            class_weight=inverse_frequency,
            symmetric_edge_features=[0, 1],
            antisymmetric_edge_features=[2],
            inference_method='qpbo')

@@

The source code is shown in Listing 1.
Lines 1--5 declare a model using parametric edge potentials for arbitrary graphs.
Here \texttt{class\_weight} re-weights the Hamming loss according to inverse class
frequencies. The parametric pairwise interactions have three features: a
constant feature, color similarity, and relative vertical position. The first two
are declared to be symmetric with respect to the direction of an edge, the last
is antisymmetric. We use fusion moves for inference.  Line 5
creates a \texttt{learner} object that will learn the parameters for the given
model using the $n$-slack cutting plane method, and line 6 performs the actual
learning.  Using this simple setup, we achieve an accuracy of 30.3 on the
validation set following the protocol of \citet{krahenbuhl2012efficient}, who
report 30.2 using a more complex approach. Training the structured model takes
approximately 30 minutes using a single i7 core.

@@

Results are shown in \Figref{timings}. We report learning times and accuracy for
varying regularization parameter $C$. The MNIST dataset has 60\,000 training
examples, 784 features and 10 classes.%
\footnote{Details about the experiment and code for the experiments can be found on the project website.}
The figure indicates that \pystruct has competitive performance, while using
a high-level interface in a dynamic programming language.

>>>>

\bottomrule
\end{tabularx}
    \caption{\label{table:comparision_algorithms}Comparison of learning
        algorithms implemented in popular structured prediction software
        packages. 1-CP stands for $1$-slack Cutting Plane, $n$-CP for $n$-slack
        Cutting plane, SSGD for stochastic subgradient decent learning of
        SSVMs, SZLJSP is as described in \secref{dual_coordinate_descent},
        L-SVM stands for latent variable SSVMs, and ML for
        maximum likelihood learning.}
\end{table}

@@

We demonstrate the use of \pystruct on the task of semantic image segmentation,
the main focus of this work. The example shows how to learn an $n$-slack support
vector machine on a superpixel-based CRF on the \textsc{Pascal VOC} dataset. Details of the experiment
can be found in \Secref{semantic_segmentation}.
Each sample (corresponding on one entry of the list \texttt{X}) is represented as a
tuple consisting of input features and a graph representation.
\begin{listing}[t]
\begin{pythoncode}
model = crfs.EdgeFeatureGraphCRF(
            class_weight=inverse_frequency,
            symmetric_edge_features=[0, 1],
            antisymmetric_edge_features=[2],
            inference_method='qpbo')

@@

The source code is shown in Listing 1.
Lines 1--5 declare a model using parametric edge potentials for arbitrary graphs.
Here \texttt{class\_weight} re-weights the Hamming loss according to inverse class
frequencies. The parametric pairwise interactions have three features: a
constant feature, color similarity, and relative vertical position. The first two
are declared to be symmetric with respect to the direction of an edge, the last
is antisymmetric. We use fusion moves for inference.  Line 5
creates a \texttt{learner} object that will learn the parameters for the given
model using the $n$-slack cutting plane method, and line 6 performs the actual
learning.  Using this simple setup, we achieve an accuracy (Jaccard index) of 30.3 on the
validation set following the protocol of \citet{krahenbuhl2012efficient}, who
report 30.2 using a more complex approach. Training the structured model takes
approximately 30 minutes using a single i7 core.

@@

Results are shown in \Figref{timings}. We report learning times and accuracy for
varying regularization parameter $C$. The MNIST dataset has $60\,000$ training
examples, $784$ features and $10$ classes.%
The setup of the experiment is the same as in Chapter~\ref{ch:comparison}.
The figure indicates that \pystruct has competitive performance, while using
a high-level interface in a dynamic programming language.
